Final draft

### 2021-07-15 final draft.Rmd
La footnote è inutile, Radon Nikodym è già illustrato

Let us consider two probability spaces: $(\X,\B(\X),\Q)$ and $(\X,\B(\X),\M)$ and let the measurable function $w:\X \rightarrow \R$ be proportional to the Radom-Nikodym derivative between $\Q$ and $\M$, i.e.,  $w(x)\propto\frac{\Q(dx)}{\M(dx)}$.\footnote{From the Radom-Nikodym theorem a sufficient condition for $w$ to exist is that $\Q$ is absolutely continuous with respect to $\M$: $\Q\ll \M$.} \
The following result represents the starting point for the idea of importance sampling.

@@

In this section, we apply the particle filter in a model-comparison
exercise, ultimately underlining the importance of taking stochastic
volatility into account in modeling equity returns.

>>>>

Let us consider two probability spaces: $(\X,\B(\X),\Q)$ and $(\X,\B(\X),\M)$ and let the measurable function $w:\X \rightarrow \R$ be proportional to the Radom-Nikodym derivative between $\Q$ and $\M$, i.e.,  $w(x)\propto\frac{\Q(dx)}{\M(dx)}$. \
The following result represents the starting point for the idea of importance sampling.

@@

In this section, we apply the particle filter in a model-comparison
exercise, ultimately underlining the importance of taking stochastic
volatility into account in modeling equity returns. We follow XX, comparing density forecasts through relative predictive and cumulative likelihoods.
